\textsf{\textbf{Drop Electro-Bouncing in Low-Gravity}}

### 2018-03-22 doc/manuscript/manuscript.tex
added summaries

%\doublespacing
\section*{Abstract}
\addcontentsline{toc}{chapter}{\numberline{Abstract}}
\noindent
We investigate the dynamics of spontaneous jumps of water droplets from electrically charged superhydrophobic dielectric substrates during a sudden step reduction in gravity level. In the brief free-fall environment of a drop tower, with a non-homogeneous external electric field (with strengths ~0.39-2.36 kV/cm) arising due to dielectric surface charges, body forces acting on the jumped droplets are primarily supplied by polarization stress and Coulombic attraction instead of gravity. This electric body force leads to a droplet bouncing behavior similar to well-known phenomena in 1-$g_0$, though occurring for much larger droplets ($\sim$ 0.5 mL). We show a simple model for the phenomenon, its scaling, and asymptotic estimates for droplet time of flight. The droplet trajectories are controlled primarily by the dimensionless electrostatic Euler number $\mathbb{E}\mbox{u}$, which is a ratio of inertial to electrostatic forces. For ${\mathbb{E}\mbox{u}}_+ \gg 1/8 \pi$ droplets escape the electric field. The droplet net charge, estimated to be on the order of $1 \times 10^{-9}$ C, is field-induced rather than occurring by contact charging at the (PTFE coated) hydrophobic interface. In 1-$g_0$, for Weber numbers $>$ 0.4, impact recoil behavior on a super-hydrophobic surface is normally dominated by damping from contact line hysteresis. However, for the low Bond and Ohnesorge numbers occurring in free-fall, the droplet impact dynamics additionally include electrohydrodynamic surface wettability effects. This is qualitatively discussed in terms of trends in coefficients of restitution and dimensionless contact time.

@@

\section{Scaling}
For small DEP forces, the equation of motion, Equation \ref{gov_eqn_subs}, is non-linear, non-homogeneous and must be solved numerically. Nevertheless we are curious if we can obtain approximate solutions to the equation analytically using perturbation methods. This is aided by non-dimensionalizing the governing equations, forming dimensionless groups, and determining whether any are particularly small or large, and whether any fortuitous opportunities for simplification appear. Introducing the scaled variables
\begin{equation}
 t^* = \frac{t}{t_c}, \hspace{10 mm} y^* = \frac{y}{y_c}, \end{equation}
where $y_c$ and $t_c$ are characteristic length and time scales respectively, and using the coordinate transformation $y(0) - R = 0$, the governing equation becomes
\begin{eqnarray}
& {y^*}'' = - \frac{1}{2} \frac{C_D \rho A y_c}{m} {y^*}'^2
- \frac{q E_0 t_c^2}{m y_c} E^* ( {y^*} ) 
- \frac{k q^2 t_c^2}{16 \pi \epsilon_0 R^2 m y_c} \left( \frac{y_c}{R} {y^*} + 1 \right)^{-2}, & \label{scaled_eqn}
\end{eqnarray}
subject to 
\begin{equation*}
{y^*}(0) = 0, \hspace{5 mm} \mbox{and} \hspace{5 mm} {y^*}'(0) = \frac{U_0 t_c}{y_c} .
\end{equation*}
We note the existence of several dimensionless groups
\[ \mathbf{\Pi}_1 = \frac{C_D \rho A y_c}{2 m}, \hspace{5 mm}
\mathbf{\Pi}_2 = \frac{q E_0 t_c^2}{m y_c}, \hspace{5 mm}
\mathbf{\Pi}_3 = \frac{k q^2 t_c^2}{16 \pi \epsilon_0 R^2 m y_c}, \hspace{5 mm}
\mathbf{\Pi}_4 = \frac{y_c}{R}, \hspace{5 mm}
\mathbf{\Pi}_5 = \frac{U_0 t_c}{y_c},\]
such that Equation \ref{scaled_eqn} becomes
\begin{equation}
\label{pi_terms}
 {y^*}'' = - \mathbf{\Pi}_1 {y^*}'^2
- \mathbf{\Pi}_2 E^* ( {y^*} ) 
- \mathbf{\Pi}_3 \left( \mathbf{\Pi}_4 {y^*} + 1 \right)^{-2},
\end{equation}
subject to
\begin{equation*}
{y^*}(0) = 0, \hspace{5 mm} \mbox{and} \hspace{5 mm} {y^*}'(0) = \mathbf{\Pi}_5 .
\end{equation*}
\begin{figure}[ht]
 \centering
 \includegraphics[width=0.75\textwidth]{../figures/apparatus0.pdf}
 \caption{A schematic representation of a drop electro-bounce experiment with labeled characteristic time and length scales, \hl{$t_c$, $y_c$} shown. Also shown are the dimensions of the superhydrophobic electret substrate.\label{fig:apparatus0}}
\end{figure}

@@

By substitution of the expansion  \ref{regular_pert} and its derivatives into \ref{pi_terms}, and equating terms by order we first find the $\mathcal{O}(1)$ unperturbed solution
\[{y^*_{0}}{\left ({t^*} \right )} = {t^*} + \frac{{t^*}^{2}}{2} \left(-1 - \mathbb{I}\mbox{g}\right). \]
Looking at this solution it is evident that if $\mathbb{I}\mbox{g}=0$, the solution is the classical kinematic equation for projectile motion without drag under constant gravity $g_0$. Continuing on with this procedure we find, after some tedious computations documented in in the project repository for this thesis\cite{schmidt_droplet_electro-bounce:_2017}, the $\mathcal{O}(\mathbb{E}\mbox{u}^5)$ order accurate solution, truncated to $\mathcal{O}(\mathbb{E}\mbox{u}^2)$ below.
\begin{eqnarray}
\label{perturb_image}
&{y^*}({t^*}) = {t^*} + \frac{{t^*}^{2}}{2} \left(-1 - \mathbb{I}\mbox{g}\right) + \mathbb{E}\mbox{u} \left(\frac{\mathbb{I}\mbox{g} {t^*}^{3}}{3} + \frac{\mathbb{I}\mbox{g} {t^*}^{4}}{12} \left(-1 - \mathbb{I}\mbox{g} \right)\right)& \\
&+ \mathbb{E}\mbox{u}^{2} \left(- \frac{\mathbb{I}\mbox{g} {t^*}^{4}}{4} + \frac{\mathbb{I}\mbox{g} \bar{t^*}^{5}}{60} \left(9 + 11 \mathbb{I}\mbox{g} \right) + \frac{\mathbb{I}\mbox{g} {t^*}^{6}}{360} \left(-9 - 20 \mathbb{I}\mbox{g} - 11 \mathbb{I}\mbox{g}^{2}\right)\right) + \mathcal{O}(\mathbb{E}\mbox{u}^3).&\nonumber
\end{eqnarray}
We plot the approximate short-time scaled solution Equation \ref{perturb_image} with varying values of $\mathbb{I}\mbox{g}$ in Figure \ref{fig:short_times}.
%\newpage
\begin{figure}[htb]
    \centering
    \resizebox{1\textwidth}{!}{\input{../figures/short_times.pgf}}
    \caption{Short-time scaled drop trajectories for various values of $\mathbb{E}\mbox{u}$, $\mathbb{I}\mbox{g}$. The trajectory reduces to the classical $\mathcal{O}(1)$ solution for small values of $\mathbb{I}\mbox{g}$. It should be noted that despite what is implied by these plots $\mathbb{I}\mbox{g}$ is not necessarily independent of $\mathbb{E}\mbox{u}$, as they share $q$, and $E_0$ as common factors, $U_0 \sim R_d^2$, and $m \sim R_d^3$.}
    \label{fig:short_times}
\end{figure}
These plots show a trend of decreasing time-of-flight $t_f$, which is the time for the drop to return to the origin, or complete a single ``bounce'', and height at apoapse with increasing values of $\mathbb{I}\mbox{g}$. When $\mathbb{I}\mbox{g} = 1$, $t_f$ is exactly half of characteristic time scale in this regime. In the limit of small $\mathbb{E}\mbox{u}$ the trajectories collapse to the $\mathcal{O}(1)$ solution regardless of the Image number. In principle there is some coupling between $\mathbb{E}\mbox{u}$ and $\mathbb{I}\mbox{g}$; notably this relationship does not depend on the electric field $E_0$ but on a charge to mass ratio. The effect of contact line hysteresis on the initial jump velocity $U_0$ will also tend to independently decohere the natural covariance between these parameters.

@@

By again applying a regular perturbation to the asymptotic solution with the expansion
\[ t^* \sim t^*_0 + B \mathbb{E}\mbox{u} t^*_1 + B^2 \mathbb{E}\mbox{u}^2 t^*_2 \ldots B^n \mathbb{E}\mbox{u}^n t^*_n  
,\]
and solving for the roots at times when $y^* = 0$, we find an asymptotic estimate for the time-of-flight. The $\mathcal{O}(B^2 \mathbb{E}\mbox{u}^2)$ accurate time-of-flight estimate is given by
\[t_f = 2 + B \mathbb{E}\mbox{u} \left(\frac{4}{3} - \frac{2 \mathbb{D}\mbox{g}}{3}\right) + B^2 \mathbb{E}\mbox{u}^{2} \left(\frac{4}{5} - \frac{4 \mathbb{D}\mbox{g}}{3} + \frac{2 \mathbb{D}\mbox{g}^{2}}{5}\right) + \mathcal{O}(B^3 \mathbb{E}\mbox{u}^3).\]
Substituting the experimental value of $\mathbb{D}\mbox{g}$ we find the time-of-flight estimate for water drops is
\begin{equation} \label{time_of_flight}
t_f = 2 + 1.333 B \mathbb{E}\mbox{u} + 0.799 B^2 \mathbb{E}\mbox{u}^{2} + \mathcal{O}(B^3 \mathbb{E}\mbox{u}^3). 
\end{equation} 
In Figure \ref{fig:drag} we see the effect of increasing values of $B \mathbb{E}\mbox{u}$ on $t_f$.
\begin{figure}[htb]
    \centering
    \input{../figures/drag.pgf}
    \caption{$\mathcal{O}(B^3 \mathbb{E}\mbox{u}^3)$ accurate asymptotic estimate of drop time-of-flight $t_f$.}
    \label{fig:drag}
\end{figure}
As $\mathbb{E}\mbox{u}$ grows to be no longer small, the time-of-flight grows rapidly, but this behavior appears to have an asymptote at a certain critical velocity; this is an electrostatic escape velocity $U_e$. We can find the escape velocity by solving a modified version of the equation of motion
\[ m u' = - \frac{q E_0 y_c^2}{y^2}, \]
where $u = \frac{d y}{d t}$ is the drop velocity. Integrating between the respective limits we find
\[m \int^{u(y)}_{U_0} u du = -q E_0 y_c^2 \int^y_{R_d} \frac{dy}{y^2} ,\]
which has the solution
\[ u(y) = \pm U_0 \left[1 + \frac{2q E_0 y_c^2}{m U_0^2} \left( \frac{1}{y} - \frac{1}{R_d} \right) \right]^{1/2}.
\]
This equation has an asymptotic velocity, $U_{\infty}$ at $y = \infty$ which is real provided 
\[ U_0 \geq  U_e = y_c \sqrt{\frac{2 q E_0 }{m R_d}},
\]
where $U_e$ is the escape velocity and $U_{\infty} = \sqrt{U_0^2 - U_e^2}$. If $y_c=L$ the condition for the drops to escape the electric field is then given by
\begin{equation}\label{escape}
\frac{1}{8 \pi} B \mathbb{E}\mbox{u} > 1.
\end{equation}
If the drop escapes the electric field it will have a residual velocity $U_{\infty}$, and will be in a regime of pure inertia $\sim$ drag. The velocity will then decay as
\[
u^*(t^*) = \frac{1}{t^* + 1},
\]
with a characteristic time $t_c \sim \frac{2 m}{C_D \rho A U_{\infty}}$, which is the halving time of the velocity.
\section{Summary}
Notes.

\chapter{Methodology}
\section{Overview}
We are concerned mainly about what parameters are important in electrostatic transport of relatively large millimetric drops in low-gravity, and what the values of the respective dimensionless numbers might be; namely, $\mathbb{I}\mbox{g}$, and $\mathbb{E}\mbox{u}$. However, this raises an interesting challenge; it is impractical to directly measure all of the key physical quantities that appear in the dimensionless groups at once in a drop tower experiment. In particular, determination of net drop free electric charge $q$, is difficult as high-input resistance electrometers are not well-suited to sudden the 15-$g_0$ decelerations characteristic of drop tower experiments. Schematic representations of drop jump statics and dynamics are shown in Figures \ref{fig:apparatus0} and \ref{fig:schematic}. To find typical values of these parameters we use the following approach:
\begin{enumerate}
\item We vary the independent variables $V_d$, and $\sigma$ in a set of single-drop spontaneous drop jumps on charged dielectric super-hydrophobic substrates under low-gravity conditions in a $2.1$ s drop tower. 
\item We capture high-speed video, and digitize the trajectories of the drops. 
\item We solve the inverse problem to find the key parameters by maximizing a statistical likelihood function between an observed trajectory and the trajectory predicted by a dynamical model given that certain set parameters.
\end{enumerate}
\begin{figure}[ht]
 \centering
 \includegraphics[width=0.65\textwidth]{../figures/schematic.pdf}
 \caption{A schematic representation of the drop initial condition, resting on the superhydrophobic surface in the Cassie-Baxter state just prior to the drop tower experiment. The variables $q$, $\sigma$, and $V_d$ are the drop net free charge, dielectric surface charge density, and drop volume respectively.\label{fig:schematic}}
\end{figure}

@@

\section{Summary}
Notes.

@@

>>>>

%\doublespacing
\section*{Abstract}
\addcontentsline{toc}{chapter}{\numberline{Abstract}}
\noindent
We investigate the dynamics of spontaneous jumps of water droplets from electrically charged superhydrophobic dielectric substrates during a sudden step reduction in gravity level. In the brief free-fall environment of a drop tower, with a non-homogeneous external electric field arising due to dielectric surface charges (with surface potentials ~0.4-1.8 kV), body forces acting on the jumped droplets are primarily supplied by polarization stress and Coulombic attraction instead of gravity. This electric body force leads to a droplet bouncing behavior similar to well-known phenomena in 1-$g_0$, though occurring for much larger droplets ($\sim$ 0.5 mL). We show a simple model for the phenomenon, its scaling, and asymptotic estimates for droplet time of flight in two regimes: firstly, in short-times close to the substrate when drop inertia balances Coulombic force due to net free charge and image charges in the dielectric substrate, and secondly, in long-times far from the substrate when drop inertia balances free charge Coulombic force and drag. The droplet trajectories are controlled primarily by the dimensionless electrostatic Euler number $\mathbb{E}\mbox{u}$, which is a ratio of inertial to electrostatic forces. To experimentally determine values of $\mathbb{E}\mbox{u}$ we conduct a series of drop tower experiments where we observe the effect of droplet volume, net free charge, and static surface potential of the superhydrophobic substrate on droplet trajectories. We use a direct search optimization to obtain a Maximum Likelihood Estimate for drop net charge, as we do not measure it directly in experiment. For $B \mathbb{E}\mbox{u} /8 \pi > 1$ droplets escape the electric field, however we do not observe any escapes in our dataset. Finally, with an eye towards engineering applications we consider the results in light of the so-called low-gravity phase separation problem with a short space system design worked example problem.

@@

\section{Scaling}
For small DEP forces, the equation of motion, Equation \ref{gov_eqn_subs}, is non-linear, non-homogeneous and must be solved numerically. Nevertheless we are curious if we can obtain approximate solutions to the equation analytically using perturbation methods. This is aided by non-dimensionalizing the governing equations, forming dimensionless groups, and determining whether any are particularly small or large, and whether any fortuitous opportunities for simplification appear. Introducing the scaled variables
\begin{equation}
 t^* = \frac{t}{t_c}, \hspace{10 mm} y^* = \frac{y}{y_c}, \end{equation}
where $y_c$ and $t_c$ are characteristic length and time scales respectively, and using the coordinate transformation $y(0) - R = 0$, the governing equation becomes
\begin{eqnarray}
& {y^*}'' = - \frac{1}{2} \frac{C_D \rho A y_c}{m} {y^*}'^2
- \frac{q E_0 t_c^2}{m y_c} E^* ( {y^*} ) 
- \frac{k q^2 t_c^2}{16 \pi \epsilon_0 R^2 m y_c} \left( \frac{y_c}{R} {y^*} + 1 \right)^{-2}, & \label{scaled_eqn}
\end{eqnarray}
subject to 
\begin{equation*}
{y^*}(0) = 0, \hspace{5 mm} \mbox{and} \hspace{5 mm} {y^*}'(0) = \frac{U_0 t_c}{y_c} .
\end{equation*}
We note the existence of several dimensionless groups
\[ \mathbf{\Pi}_1 = \frac{C_D \rho A y_c}{2 m}, \hspace{5 mm}
\mathbf{\Pi}_2 = \frac{q E_0 t_c^2}{m y_c}, \hspace{5 mm}
\mathbf{\Pi}_3 = \frac{k q^2 t_c^2}{16 \pi \epsilon_0 R^2 m y_c}, \hspace{5 mm}
\mathbf{\Pi}_4 = \frac{y_c}{R}, \hspace{5 mm}
\mathbf{\Pi}_5 = \frac{U_0 t_c}{y_c},\]
such that Equation \ref{scaled_eqn} becomes
\begin{equation}
\label{pi_terms}
 {y^*}'' = - \mathbf{\Pi}_1 {y^*}'^2
- \mathbf{\Pi}_2 E^* ( {y^*} ) 
- \mathbf{\Pi}_3 \left( \mathbf{\Pi}_4 {y^*} + 1 \right)^{-2},
\end{equation}
subject to
\begin{equation*}
{y^*}(0) = 0, \hspace{5 mm} \mbox{and} \hspace{5 mm} {y^*}'(0) = \mathbf{\Pi}_5 .
\end{equation*}
\begin{figure}[ht]
 \centering
  \input{../figures/apparatus01.pdf_tex}
 \caption{A schematic representation of a drop electro-bounce experiment with labeled characteristic time and length scales, \hl{$t_c$, $y_c$} shown. Also shown are the dimensions of the superhydrophobic electret substrate.\label{fig:apparatus0}}
\end{figure}

@@

By substitution of the expansion  \ref{regular_pert} and its derivatives into \ref{pi_terms}, and equating terms by order we first find the $\mathcal{O}(1)$ unperturbed solution
\[{y^*_{0}}{\left ({t^*} \right )} = {t^*} + \frac{{t^*}^{2}}{2} \left(-1 - \mathbb{I}\mbox{g}\right). \]
Looking at this solution it is evident that if $\mathbb{I}\mbox{g}=0$, the solution is the classical kinematic equation for projectile motion without drag under constant gravity $g_0$. Continuing on with this procedure we find, after some tedious computations documented in in the project repository for this thesis\cite{schmidt_droplet_electro-bounce:_2017}, the $\mathcal{O}(\mathbb{E}\mbox{u}^5)$ order accurate solution, truncated to $\mathcal{O}(\mathbb{E}\mbox{u}^2)$ below.
\begin{eqnarray}
\label{perturb_image}
&{y^*}({t^*}) = {t^*} + \frac{{t^*}^{2}}{2} \left(-1 - \mathbb{I}\mbox{g}\right) + \mathbb{E}\mbox{u} \left(\frac{\mathbb{I}\mbox{g} {t^*}^{3}}{3} + \frac{\mathbb{I}\mbox{g} {t^*}^{4}}{12} \left(-1 - \mathbb{I}\mbox{g} \right)\right)& \\
&+ \mathbb{E}\mbox{u}^{2} \left(- \frac{\mathbb{I}\mbox{g} {t^*}^{4}}{4} + \frac{\mathbb{I}\mbox{g} \bar{t^*}^{5}}{60} \left(9 + 11 \mathbb{I}\mbox{g} \right) + \frac{\mathbb{I}\mbox{g} {t^*}^{6}}{360} \left(-9 - 20 \mathbb{I}\mbox{g} - 11 \mathbb{I}\mbox{g}^{2}\right)\right) + \mathcal{O}(\mathbb{E}\mbox{u}^3).&\nonumber
\end{eqnarray}
We plot the approximate short-time scaled solution Equation \ref{perturb_image} with varying values of $\mathbb{I}\mbox{g}$ in Figure \ref{fig:short_times}.
%\newpage
\begin{figure}[htb]
    \centering
    \resizebox{1\textwidth}{!}{\input{../figures/short_times.pgf}}
    \caption{Short-time scaled drop trajectories for various values of $\mathbb{E}\mbox{u}$, $\mathbb{I}\mbox{g}$. The trajectory reduces to the classical $\mathcal{O}(1)$ solution for small values of $\mathbb{I}\mbox{g}$. It should be noted that despite what is implied by these plots $\mathbb{I}\mbox{g}$ is not necessarily independent of $\mathbb{E}\mbox{u}$, as they share $q$, and $E_0$ as common factors, $U_0 \sim R_d^2$, and $m \sim R_d^3$.}
    \label{fig:short_times}
\end{figure}
These plots show a trend of decreasing time-of-flight $t_f$, which is the time for the drop to return to the origin, or complete a single `bounce', and height at apoapse with increasing values of $\mathbb{I}\mbox{g}$. When $\mathbb{I}\mbox{g} = 1$, $t_f$ is exactly half of characteristic time scale in this regime. In the limit of small $\mathbb{E}\mbox{u}$ the trajectories collapse to the $\mathcal{O}(1)$ solution regardless of the Image number. In principle there is some coupling between $\mathbb{E}\mbox{u}$ and $\mathbb{I}\mbox{g}$; notably this relationship does not depend on the electric field $E_0$ but on a charge to mass ratio. The effect of contact line hysteresis on the initial jump velocity $U_0$ will also tend to independently decohere the natural covariance between these parameters.

@@

By again applying a regular perturbation to the asymptotic solution with the expansion
\[ t^* \sim t^*_0 + B \mathbb{E}\mbox{u} t^*_1 + B^2 \mathbb{E}\mbox{u}^2 t^*_2 \ldots B^n \mathbb{E}\mbox{u}^n t^*_n  
,\]
and solving for the roots at times when $y^* = 0$, we find an asymptotic estimate for the time-of-flight. The $\mathcal{O}(B^2 \mathbb{E}\mbox{u}^2)$ accurate time-of-flight estimate is given by
\[t_f = 2 + B \mathbb{E}\mbox{u} \left(\frac{4}{3} - \frac{2 \mathbb{D}\mbox{g}}{3}\right) + B^2 \mathbb{E}\mbox{u}^{2} \left(\frac{4}{5} - \frac{4 \mathbb{D}\mbox{g}}{3} + \frac{2 \mathbb{D}\mbox{g}^{2}}{5}\right) + \mathcal{O}(B^3 \mathbb{E}\mbox{u}^3).\]
Substituting the experimental value of $\mathbb{D}\mbox{g}$ we find the time-of-flight estimate for water drops is
\begin{equation} \label{time_of_flight}
t_f = 2 + 1.333 B \mathbb{E}\mbox{u} + 0.799 B^2 \mathbb{E}\mbox{u}^{2} + \mathcal{O}(B^3 \mathbb{E}\mbox{u}^3). 
\end{equation} 
In Figure \ref{fig:drag} we see the effect of increasing values of $B \mathbb{E}\mbox{u}$ on $t_f$.
\begin{figure}[htb]
    \centering
    \input{../figures/drag.pgf}
    \caption{$\mathcal{O}(B^3 \mathbb{E}\mbox{u}^3)$ accurate asymptotic estimate of drop time-of-flight $t_f$.}
    \label{fig:drag}
\end{figure}
As $\mathbb{E}\mbox{u}$ grows to be no longer small, the time-of-flight grows rapidly, but this behavior appears to have an asymptote at a certain critical velocity; this is an electrostatic escape velocity $U_e$. We can find the escape velocity by solving a modified version of the equation of motion
\[ m u' = - \frac{q E_0 y_c^2}{y^2}, \]
where $u = \frac{d y}{d t}$ is the drop velocity. Integrating between the respective limits we find
\[m \int^{u(y)}_{U_0} u du = -q E_0 y_c^2 \int^y_{R_d} \frac{dy}{y^2} ,\]
which has the solution
\[ u(y) = \pm U_0 \left[1 + \frac{2q E_0 y_c^2}{m U_0^2} \left( \frac{1}{y} - \frac{1}{R_d} \right) \right]^{1/2}.
\]
This equation has an asymptotic velocity, $U_{\infty}$ at $y = \infty$ which is real provided 
\[ U_0 \geq  U_e = y_c \sqrt{\frac{2 q E_0 }{m R_d}},
\]
where $U_e$ is the escape velocity and $U_{\infty} = \sqrt{U_0^2 - U_e^2}$. If $y_c=L$ the condition for the drops to escape the electric field is then given by
\begin{equation}\label{escape}
\frac{B}{8 \pi} \mathbb{E}\mbox{u} > 1.
\end{equation}
If the drop escapes the electric field it will have a residual velocity $U_{\infty}$, and will be in a regime of pure inertia $\sim$ drag. The velocity will then decay as
\[
u^*(t^*) = \frac{1}{t^* + 1},
\]
with a characteristic time $t_c \sim \frac{2 m}{C_D \rho A U_{\infty}}$, which is the halving time of the velocity.
\section{Summary}
The objective of this work is to understand the basic physics of the low-gravity drop bounce phenomenon to the point where we can make useful predictions of drop behavior for engineering purposes. To that end, in this chapter we have shown the following:
\begin{itemize}
\item We develop from first principles a simple 1-dimensional model of drop trajectories subject to Coulombic forces and drag under low-gravity. Drops are idealized as point charges. We find that polarization stresses are negligible, and that water drops can be modeled as ideal conductors under the conditions of our experiments.
\item By scaling arguments we find characteristic length and time scales for both a short-times regime where inertia balances Coulombic force and forces due to image charges, and a long-times regime where inertia balances Coulombic force and drag. In both regimes a key dimensionless group appears: the electrostatic Euler number $\mathbb{E}\mbox{u}$, which is a ratio of inertia to electrostatic force. 
\item The governing ODE is non-linear, but we find approximate analytic solutions for the drop trajectory and time of flight in both regimes by means of asymptotic expansions.
\item We find a limiting initial velocity $U_0$ for which drop time of flight grows without bound. This electrostatic escape velocity is analogous to the gravitational escape velocity of a planet or other massive body. 
\end{itemize}

\chapter{Methodology}
\section{Overview}
We are interested mainly about which parameters are important in electrostatic transport of relatively large millimetric drops in low-gravity, and what the values of the respective dimensionless numbers might be; namely, $\mathbb{I}\mbox{g}$, and $\mathbb{E}\mbox{u}$. However, this raises an interesting challenge; it is impractical to directly measure all of the key physical quantities that appear in the dimensionless groups at once in a drop tower experiment. In particular, determination of net drop free electric charge $q$, is difficult as high-input resistance electrometers are not well-suited to sudden the 15-$g_0$ decelerations characteristic of drop tower experiments. Schematic representations of drop jump statics and dynamics are shown in Figures \ref{fig:apparatus0} and \ref{fig:schematic}. To find typical values of these parameters we use the following approach:
\begin{enumerate}
\item We vary the independent variables $V_d$, and $\sigma$ in a set of single-drop spontaneous drop jumps on charged dielectric super-hydrophobic substrates under low-gravity conditions in a $2.1$ s drop tower. 
\item We capture high-speed video, and digitize the trajectories of the drops. 
\item We solve the inverse problem to find the key parameters by maximizing a statistical likelihood function between an observed trajectory and the trajectory predicted by a dynamical model given that certain set parameters.
\end{enumerate}
\begin{figure}[ht]
 \centering
 \includegraphics[width=0.65\textwidth]{../figures/schematic.pdf}
 \caption{A schematic representation of the drop initial condition, resting on the superhydrophobic surface in the Cassie-Baxter state just prior to the drop tower experiment. The variables $q$, $\sigma$, and $V_d$ are the drop net free charge, dielectric surface charge density, and drop volume respectively.\label{fig:schematic}}
\end{figure}

@@

\section{Summary}
The objectives of our experimental work are to validate the earlier scaling results by identifying values of the physical parameters which appear in the relevant dimensionless groups. To accomplish this we conduct a series of low-gravity experiments in a 2.1 s drop tower, where we observe the trajectories of spontaneous drop jumps and rebounds from charged dielectric superhydrophobic substrates.
\begin{itemize}
\item  In drop tower experiments we vary the independent variables $V_d$ and $\sigma$ and capture the trajectories of the droplets using high-speed video. 
\item We produce superhydrophobic electret substrates with surface potentials 0.7-4.0 $kV$ and contact angles $\sim 150^{\circ}$ with approximately $25^{\circ}$ contact angle hysteresis when uncharged. The dielectrics are a lamina of 3-4 corona charged 0.4 mm PMMA sheets. The electric field scales with the number of dielectric lamina. The superhydrophobic layer of the electret lamina is manufactured by laser etching a $\sim$775 $\mu$m deep square array of pillars into the PMMA sheet, followed by a PTFE spray deposition process. 
\item We solve the inverse problem to identify key parameters which we cannot measure directly in the drop tower experiments. This is accomplished by Maximum Likelihood Estimation using constrained direct search optimization.
\item We fail to establish the identifiability of the parameter estimate using the conventional approach of inverting the Hessian near the optima. This indicates ill-conditioning of the parameter estimation problem, likely due to large multicolinearity between the main factors $q$, $V_d$ and $\sigma$. To robustly estimate the error of the parameter estimates an alternate approach, such as the Monte Carlo method, is required.
\end{itemize}

@@

In 1-$g_0$, for Weber numbers $>$ 0.4, impact recoil behavior on a super-hydrophobic surface is normally dominated by damping from contact line hysteresis. However, for the low Bond and Ohnesorge numbers occurring in free-fall, the droplet impact dynamics additionally include electrohydrodynamic surface wettability effects. This is qualitatively discussed in terms of trends in coefficients of restitution and dimensionless contact time.
